Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-04 programlogic.tex
+

\begin{figure}
   \includegraphics[width=\columnwidth]{addr_space_switch.png}
  \caption{Loading an Address-Space into the Current Memory View}
  \label{fig:addrswitch}
  \end{figure}

In Figure \ref{fig:addrswitch}, we see two different address-spaces rooted at R0 and R1 in the pre/post condition. To be put into words, while switching an address-space by executing \lstinline|mov_ctl|) updating the $\crthree$, it is expected to mention resources of two different address-spaces in the specification. In the precondition, the dashed white background denotes the resources of the current address space: $\crthree$ is loaded with R0 and all the virtual-pointsto assertions ($a_0 \mapsto_{\textsf{v}}p_0$ and $a_1 \mapsto_{\textsf{v}}p_1$). We need one more address-space -- the solid square with the root address R1 -- which has its own resources ($b_0 \mapsto_{\textsf{v}}p_3$ and $b_1 \mapsto_{\textsf{v}}p_4$) which are invalid under the current address space rooted at R0. This pattern of specification requires resources being mentioned under the \textit{world} they are valid, i.e. a modal-framing within the specification. Once the current address-space becomes the one with root address R1, i.e. $\crthree$ is loaded with R1, the context-resources $b_0 \mapsto_{\textsf{v}}p_3$ and $b_1 \mapsto_{\textsf{v}}p_4$ are loaded into the current-view of the memory, and all the other resources that are valid under R0 are introduced into the modal context rooted at R0
\[
\begin{array}{l}
  \{ \crthree \mapsto_{r} R0 \ast a_0 \mapsto_{\textsf{v}}p_0  \ast a_1 \mapsto_{\textsf{v}}p_1  \ast [r1]\;( b_0 \mapsto_{\textsf{v}}p_3  \ast b_1 \mapsto_{\textsf{v}}p_4 )\}\\
  \qquad \qquad \qquad \qquad\qquad \qquad \mathsf{mov\_ctl} \;\; \crthree \; \; R1\\

  \{ \crthree \mapsto_{r} R1 \ast [r0](a_0 \mapsto_{\textsf{v}}p_0  \ast a_1 \mapsto_{\textsf{v}}p_1)  \ast  b_0 \mapsto_{\textsf{v}}p_3  \ast b_1 \mapsto_{\textsf{v}}p_4 \}
  \end{array}
\]
\begin{remark}[The Choice of Modal Context Definition as a Pattern of Verification Context]
  \label{remark:pattern}
  By choosing the contingency and what defines the modal contex, we simply introduce 
  \begin{enumerate}
  \item how a modal context (e.g. a address-space modality $[r]P$), logically, draws the attention to the certain facts in the interest of reasoning (e.g. virtual pointsto relations in the current address-space in Figure \ref{fig:virtualpointstosharing})
  \item and, offloads the burden of individual bookkeeping of these facts (e.g. virtual pointsto relations per address-space) under different context (e.g. virtual pointsto relations in other address-spaces) via utilizing the \textit{summarization} aspect of the contingency it represents (e.g. other virtual pointsto relations are valid under other certain address-space page-table root addresseses).  
  \end{enumerate}
\end{remark}
\paragraph{Interaction}
\label{sec:interaction}
\subsubsection{Address-Space Modality}
\label{sec:aspacemodalist}
The truth on an address space, exhibits itself as a contingent truth: a location virtualization assertion (a virtual points-to in \ref{fig:virtualpointstosharing}),  happens to valid in the \textit{current world} (in the current address space), and switching address spaces pulls information out of one \textit{world} into the “current view” of memory, and leaves other assertions true relative to the previous address space.

@@

>>>>

In Figure \ref{fig:addrswitch}, we see two different address-spaces rooted at R0 and R1 in the pre/post condition. To be put into words, while switching an address-space by executing \lstinline|mov_ctl|) updating the $\crthree$, it is expected to mention resources of two different address-spaces in the specification. In the precondition, $\crthree$ is loaded with R0 and all the virtual-pointsto assertions $a_0 \mapsto_{\textsf{v}}p_0$ and $a_1 \mapsto_{\textsf{v}}p_1$ are in the current-view of the memory and valid in the ambient logic \textsf{vProp}. The other address-space with the root address R1 has its own resources ($b_0 \mapsto_{\textsf{v}}p_3$ and $b_1 \mapsto_{\textsf{v}}p_4$) which are invalid under the current address space rooted at R0. This pattern of specification requires resources being mentioned under the \textit{world} they are valid, i.e. a modal-framing within the specification. Once the current address-space becomes the one with root address R1, i.e. $\crthree$ is loaded with R1, the context-resources $b_0 \mapsto_{\textsf{v}}p_3$ and $b_1 \mapsto_{\textsf{v}}p_4$ are loaded into the current-view of the memory, and all the other resources that are valid under R0 are introduced into the modal context rooted at R0

\begin{figure}
\[
\begin{array}{l}
  \{ \crthree \mapsto_{r} R0 \ast a_0 \mapsto_{\textsf{v}}p_0  \ast a_1 \mapsto_{\textsf{v}}p_1  \ast [r1]\;( b_0 \mapsto_{\textsf{v}}p_3  \ast b_1 \mapsto_{\textsf{v}}p_4 )\}\\
  \qquad \qquad \qquad \qquad\qquad \qquad \mathsf{mov\_ctl} \;\; \crthree \; \; R1\\

  \{ \crthree \mapsto_{r} R1 \ast [r0](a_0 \mapsto_{\textsf{v}}p_0  \ast a_1 \mapsto_{\textsf{v}}p_1)  \ast  b_0 \mapsto_{\textsf{v}}p_3  \ast b_1 \mapsto_{\textsf{v}}p_4 \}
  \end{array}
\]
  \label{fig:addrswitch}
  \end{figure}

\begin{remark}[The Choice of Modal Context, Contingency and  Pattern of Verification Context]
  \label{remark:pattern}
The truth on an address space, exhibits itself as a contingent truth: a location virtualization assertion (a virtual points-to in \ref{fig:virtualpointstosharing}),  happens to valid in the \textit{current world} (in the current address space), and switching address spaces pulls information out of one \textit{world} into the “current view” of memory, and leaves other assertions true relative to the previous address space.

@@

Pragmatically, 
  \begin{enumerate}
  \item a modal context (e.g. a address-space modality $[r]P$), logically, draws the attention to the certain facts in the interest of reasoning (e.g. virtual pointsto relations in the current address-space in Figure \ref{fig:virtualpointstosharing})
  \item and, offloads the burden of individual bookkeeping of these facts (e.g. virtual pointsto relations per address-space) under different context (e.g. virtual pointsto relations in other address-spaces) via utilizing the \textit{summarization} aspect of the contingency it represents (e.g. other virtual pointsto relations are valid under other certain address-space page-table root addresseses).  
  \end{enumerate}
\end{remark}
